An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-28 draft.tex
Write BBOB correctly

% Explain that heterogeneity comes from using different algorithms,
% not from using different types of nodes - JJ
But this is a rule of thumb, and it will depend on the degree of
heterogeneity, as well as on the algorithm itself. In this experiment, we compare the performance of both heterogeneous and
homogeneous settings. We compare a multi-population with only  GA and PSO
populations, versus an ensemble of GA and PSO algorithms on the first five
functions of the BOBB testbed.  We used ten populations and 8 workers for the
experiment and the same parameters as before.

>>>>

% Explain that heterogeneity comes from using different algorithms,
% not from using different types of nodes - JJ
But this is a rule of thumb, and it will depend on the degree of
heterogeneity, as well as on the algorithm itself. In this experiment, we compare the performance of both heterogeneous and
homogeneous settings. We compare a multi-population with only  GA and PSO
populations, versus an ensemble of GA and PSO algorithms on the first five
functions of the BBOB testbed.  We used ten populations and 8 workers for the
experiment and the same parameters as before.
